Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-14 paper.qmd
Updated NLDR data point colours

nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#6a3d9a", size = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)
```

@@

hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts, 
  aes(x = x, y = y)) +
  geom_polygon(color = "black", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5, size = 0.5, color = "#6a3d9a") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b", sc_ltr_pos)
```

@@

umap_pbmc <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.3, color = "#6a3d9a") 
```

@@

tsne_pbmc <- tsne_pbmc_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.3, color = "#6a3d9a")
```

@@

trimesh_removed_pbmc <- vis_rmlg_mesh(
  distance_edges = distance_pbmc,
  benchmark_value = benchmark_pbmc,
  tr_coord_df = tr_from_to_df_pbmc,
  distance_col = "distance") +
  geom_point(
    data = tsne_pbmc_scaled,
    aes(
      x = tSNE1,
      y = tSNE2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#6a3d9a"
  ) +
  theme_void() #+
  #xlim(sc_xlims) + ylim(sc_ylims) +
  #interior_annotation("a", sc_ltr_pos)

@@

pacmap_plot_mnist <- pacmap_minst_scaled |> 
  ggplot(aes(x = PaCMAP1, 
             y = PaCMAP2)) + 
  geom_point(alpha=0.1, color = "#6a3d9a")

>>>>

nldr_scurve <- umap_scurve_scaled |> 
  ggplot(aes(x = UMAP1, y = UMAP2)) + 
  geom_point(alpha=0.5, colour="#000000", size = 0.5) +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("a", sc_ltr_pos)
```

@@

hex_grid_scurve <- ggplot(
  data = hex_grid_with_counts, 
  aes(x = x, y = y)) +
  geom_polygon(color = "black", 
               aes(group = hex_poly_id), 
               fill = "#ffffff") +
  geom_point(data = umap_scurve_scaled, 
             aes(x = UMAP1, y = UMAP2), 
             alpha = 0.5, size = 0.5, color = "#000000") +
  xlim(sc_xlims) + ylim(sc_ylims) +
  interior_annotation("b", sc_ltr_pos)
```

@@

umap_pbmc <- umap_pbmc_scaled |>
  ggplot(aes(x = UMAP1,
             y = UMAP2)) +
  geom_point(alpha=0.3, color = "#000000") 
```

@@

tsne_pbmc <- tsne_pbmc_scaled |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.3, color = "#000000")
```

@@

trimesh_removed_pbmc <- vis_rmlg_mesh(
  distance_edges = distance_pbmc,
  benchmark_value = benchmark_pbmc,
  tr_coord_df = tr_from_to_df_pbmc,
  distance_col = "distance") +
  geom_point(
    data = tsne_pbmc_scaled,
    aes(
      x = tSNE1,
      y = tSNE2
    ),
    alpha = 0.3,
    size = 0.1,
    color = "#000000"
  ) +
  theme_void() #+
  #xlim(sc_xlims) + ylim(sc_ylims) +
  #interior_annotation("a", sc_ltr_pos)

@@

pacmap_plot_mnist <- pacmap_minst_scaled |> 
  ggplot(aes(x = PaCMAP1, 
             y = PaCMAP2)) + 
  geom_point(alpha=0.1, color = "#000000")
